---
author: "Fernando Mateos-González"
date: Last update "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    code_download: true
    toc: yes
    toc_float:
      collapsed: no
      smooth_scroll: no
      df_print: paged
  md_document:
    variant: markdown_github
  pdf_document:
    toc: yes
title: "Work sheets"


# title: "Work sheets"
# author: "Fernando Mateos-González"
# date: "`r format(Sys.time(), '%d %B, %Y')`"
# output:
#   word_document:
#     toc: no
#     fig_caption: true
#     reference_docx: styleword.docx
# 
#   

knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "output") })
  
---

```{r global_options, echo=FALSE}
# knitr::opts_chunk$set(fig.width=6, fig.asp = 0.618, fig.path='output/figs/',
#                       echo=TRUE, warning=FALSE, message=FALSE, cache= FALSE)


options(allow_html_in_all_outputs=TRUE)
```


# Library

```{r library, message=FALSE, warning=FALSE}
# install.packages("pacman")
# writeLines(pacman::p_lib(), "~/Desktop/list_of_R_packages.csv") # to quickly back up packages
# remotes::install_github("ThinkR-open/remedy")


pacman::p_load(tidyverse,janitor, data.table, here, rio, lubridate,writexl,
               gtsummary,  #to make tables
               flextable,  #to save tables in word
               clockify,   #API to get data
               plyr       # to use function round_any
)


```

# Data google sheets

```{r}

# googledrive::drive_download("worksheet", type ="csv", here("data", "worksheet.csv"))
# 
# 
# worksheet <- googledrive::drive_get("worksheet") %>% 
#   googlesheets4::read_sheet() %>% 
#   dplyr::mutate(month = lubridate::month(date, label = T)) %>% 
#   dplyr::mutate(day = lubridate::day(date)) %>% 
#   dplyr::mutate(year = lubridate::year(date)) %>% 
#   dplyr::mutate(time = as.numeric(time))
# 
# 
# by_date <- worksheet %>% 
#   dplyr::filter(month =="Jan") %>% 
#   dplyr::group_by(date) %>% 
#   dplyr::mutate(time = sum(time)) %>% 
#   dplyr::mutate(tasks_day = paste0(task,collapse = ", ")) %>% 
#   dplyr::select(year, day, month, tasks_day,time, date) %>% 
#   dplyr::distinct() %>% 
#   dplyr::ungroup() %>% 
#   dplyr::select(!date)
# 
# 
# 
#  # nando_timesheet <- googlesheets4::gs4_create(
#  #    "nando_timesheet",
#  #    sheets = "January")
#   
#  googlesheets4::sheet_write(by_date, ss = nando_timesheet, sheet = "January")
 
   


```

# Data clockify

Environment variables
https://cran.r-project.org/web/packages/httr/vignettes/secrets.html

Asking each time is a hassle, so you might want to store the secret across sessions. One easy way to do that is with environment variables. Environment variables, or envvars for short, are a cross platform way of passing information to processes.

For passing envvars to R, you can list name-value pairs in a file called .Renviron in your home directory. The easiest way to edit it is to run:

file.edit("~/.Renviron")

The file looks something like

VAR1 = value1
VAR2 = value2

And you can access the values in R using Sys.getenv():

Sys.getenv("VAR1")
 [1] "value1"

Note that .Renviron is only processed on startup, so you’ll need to restart R to see changes.

These environment variables will be available in every running R process, and can easily be read by any other program on your computer to access that file directly. For more security, use the keyring package.

```{r}

clock_keys <- Sys.getenv("clock_keys")

set_api_key(clock_keys)

projects <- clockify::projects()

data_clock<- clockify::time_entries(concise = F) 

full <- data_clock %>% 
  dplyr::left_join(projects, by= "project_id") %>% 
  dplyr::select(description, project_name, time_start, time_end, duration, billable.x) %>% 
  dplyr::mutate(date = lubridate::date(time_start)) %>% 
  dplyr::mutate(month = lubridate::month(date, label = T)) %>% 
  dplyr::mutate(day = lubridate::day(date)) %>% 
  dplyr::mutate(year = lubridate::year(date))








katka <- full %>% 
  dplyr::rename(task = description,
                project = project_name,
                hours = duration,
                for_alka = billable.x) %>% 
  dplyr::filter(for_alka == "TRUE") %>%  # only alka work
    dplyr::mutate(hours = plyr::round_any(hours/60, 0.5, f = ceiling )) %>% 
  dplyr::group_by(date) %>% 
  dplyr::mutate(total = sum(hours)) %>% 
  dplyr::mutate(tasks_day = paste0(task,collapse = ", ")) %>% 
  dplyr::group_by(date, project) %>% 
  dplyr::mutate(hours_each_project = sum(hours)) %>% 
  dplyr::select(year,month, day, date, tasks_day, project,for_alka, hours_each_project, total) %>% 
  dplyr::distinct() %>% 
  tidyr::pivot_wider(names_from = project, 
                   values_from = hours_each_project) %>% 
  dplyr::select(!for_alka) %>% 
  replace(is.na(.), 0)



# Load the google sheet

nando_timesheet <- googledrive::drive_get("nando_timesheet")

#add a new tab for the new month

katka %>% 
  dplyr::filter(month == "Feb") %>% # Select the month
  dplyr::select(!c(year,month,day)) %>% 
 googlesheets4::sheet_write(ss = nando_timesheet, sheet = "February") #create the new tab

# Review the data!
 
  
  







```

